Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
fix triangle densities

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
triangles (density $1.11\times10^{-4}$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^{-5}$ $N/\text{\AA}$) 
triangles: the computed results show no discernible difference.

>>>>

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
 to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
 the computed results show no discernible difference.
